---
title: "linear model from Web"
author: "Annabelle Polack"
date: "Summer 2022"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS


### scatterplot
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
```{r}
basicNN + geom_point()
```

It looks like there is an obvious linear relationship between SIMS and ARM. This means that the greater the arm strength of the worker, the better they preform on the simulations that were used to assess job performance. 

### Numerical results
```{r}
cor(SIMS~ARM,data=data)
```

The correlation coefficient is somewhat close to 1 showing a decent linear relationship between SIMS and ARM. 

### Inferential  (Build model.1)
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```


#### Predict at target point

```{r}
Targetpoint<- data.frame(ARM=88, GRIP=94)
```

```{r}
predict(model.1, Targetpoint, interval = "prediction")

```

This predicted the value we would get from model 1 if the target point for ARM is 88 and GRIP is 94. But given that this model only makes use of ARM, it disreguards the target point value for GRIP.

#### scatterplot with model fit

```{r}
basicNN + geom_point()+geom_lm()
```
  

## Model 2 SIM~GRIP

### Now add in scatterplot


### Numerical results 


### Inferential  (Build model.2)
  

#### predict model.2 at target point

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

